Parallel Test

### 2025-04-28 ParallelTest.Rmd
fix bug in this demo too

```{r, eval=FALSE}
sub.dir = "Results"
dir.create(file.path(getwd(), sub.dir), recursive = TRUE)

@@

  mod = loop_through_fn(om = om_with_data,
                            em_info = info, 
                            random = random,
                            M_em = M, # use OM M
                            sel_em = sel, # use OM sel
                            NAA_re_em = NAA_re_em, # use rec assumed random around the mean instead, help runtime (est B-H is difficult)
                            move_em = NULL,
                            age_comp_em = "multinomial",
                            # Here is the correct code: separate.em = FALSE also works for one-area model
                            em.opt = list(separate.em = FALSE, separate.em.type = 1, 
                                          do.move = FALSE, est.move = FALSE),
                            # ------------------------------------------------------ #
                            # - Below is needed when making changes on data quality- #
                            # ------------------------------------------------------ #
                            update_index_info  = list(agg_index_sigma = agg_index_sigma, index_Neff = index_Neff), # Must have this!
                            update_catch_info  = list(agg_catch_sigma = agg_catch_sigma, catch_Neff = catch_Neff), # Must have this!
                            # ------------------------------------------------------ #
                            # - Above is needed when making changes on data quality- #
                            # ------------------------------------------------------ #
                            assess_years = assess.years, 
                            assess_interval = assess.interval, 
                            base_years = base.years,
                            year.use = 30, # number of years of data you want to use in the assessment model
                            add.years = TRUE, # extends assessment time series instead of moving window of year.use years
                            seed = 123,
                            save.sdrep = FALSE, 
                            save.last.em = TRUE,
                            FXSPR_init = 0.01) # IMPORTANT!

>>>>

```{r, eval=FALSE}
sub.dir = "Results_test"
dir.create(file.path(getwd(), sub.dir), recursive = TRUE)

@@

  mod = loop_through_fn(om = om_with_data,
                            em_info = info, 
                            random = random,
                            M_em = M, # use OM M
                            sel_em = sel, # use OM sel
                            NAA_re_em = NAA_re_em, # use rec assumed random around the mean instead, help runtime (est B-H is difficult)
                            move_em = NULL,
                            age_comp_em = "multinomial",
                            # Here is the correct code: separate.em = FALSE also works for one-area model
                            em.opt = list(separate.em = FALSE, separate.em.type = 1, 
                                          do.move = FALSE, est.move = FALSE),
                            # ------------------------------------------------------ #
                            # - Below is needed when making changes on data quality- #
                            # ------------------------------------------------------ #
                            update_index_info  = list(agg_index_sigma = agg_index_sigma, index_Neff = index_Neff), # Must have this!
                            update_catch_info  = list(agg_catch_sigma = agg_catch_sigma, catch_Neff = catch_Neff), # Must have this!
                            # ------------------------------------------------------ #
                            # - Above is needed when making changes on data quality- #
                            # ------------------------------------------------------ #
                            assess_years = assess.years, 
                            assess_interval = assess.interval, 
                            base_years = base.years,
                            year.use = 30, # number of years of data you want to use in the assessment model
                            add.years = TRUE, # extends assessment time series instead of moving window of year.use years
                            seed = 123+i,
                            save.sdrep = FALSE, 
                            save.last.em = TRUE,
                            FXSPR_init = 0.01) # IMPORTANT!
